\documentclass[a4paper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.85in}
\addtolength{\textheight}{1.85in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]
\titlespacing{\section}{0pt}{10pt}{8pt}

% Ensure PDF is machine readable / ATS parsable
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-3pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabularx}{0.97\textwidth}[t]{@{}X r@{}}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabularx}\vspace{-9pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabularx}{0.97\textwidth}{@{}X r@{}}
      \small#1 & #2 \\
    \end{tabularx}\vspace{-9pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.18in, itemsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-9pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Sowjanya SK Susarla} \\ \vspace{3pt}
    \small B.E. Computer Science \& Engineering $\vert$ CBIT, Hyderabad $\vert$ CGPA 8.75/10 \\ \vspace{2pt}
    \small \href{mailto:kameshwarisowjanya@gmail.com}{kameshwarisowjanya@gmail.com} $\vert$
    +91-7989218633 $\vert$
    Hyderabad, India $\vert$
    \href{https://github.com/Sowjanya12125}{github.com/Sowjanya12125} $\vert$
    \href{https://www.linkedin.com/in/sowjanya-s-k-susarla-498632308/}{linkedin.com/in/sowjanya-s-k-susarla}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small{Computer Science Engineering student with a working foundation across Data Structures \& Algorithms, OOP, Operating Systems, and DBMS, plus hands-on experience building REST-API-driven, modular software systems. Track record of shipping production-grade projects under tight deadlines, comfortable across the full SDLC using Git-based version control, with additional depth in ML pipelines, data engineering, and cybersecurity risk analytics --- from architecting a credit-risk classifier to conducting enterprise-scale security assessments at India Post. Strong analytical, problem-solving orientation.}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=1pt]
    \small{\item{
     \textbf{Programming Languages}{: Python (proficient), SQL, JavaScript (basic)} \\
     \textbf{CS Fundamentals}{: Data Structures \& Algorithms (Arrays, Strings, Stacks, HashMaps, Two Pointers, Sliding Window --- in progress), Object-Oriented Programming (OOP), Operating Systems, Database Management Systems (DBMS)} \\
     \textbf{Software Engineering}{: REST APIs, Modular Architecture, Git / GitHub, Software Development Lifecycle (SDLC), Reproducible Workflow Design, API Integration} \\
     \textbf{Data \& Databases}{: SQL, MongoDB (NoSQL), Pandas, NumPy, ETL Pipelines, Matplotlib, Seaborn, Jupyter Notebook} \\
     \textbf{ML / AI}{: Scikit-learn, TensorFlow, XGBoost, SHAP, Bayesian Inference, Feature Engineering, Classification, Regression, Uncertainty Quantification} \\
     \textbf{Cybersecurity}{: Security Posture Assessment, Risk Pattern Analysis, Threat Modelling, Probabilistic Risk Frameworks, Anomaly Detection} \\
     \textbf{Domains}{: Credit Risk Modelling, Financial Analytics, Quantitative Risk, Security Data Analysis}
    }}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Research Intern --- Security \& Risk Analytics}{}
{India Post, CEPT, Hyderabad}{Jul 2025}
\resumeItemListStart
\resumeItem{Ran an end-to-end security posture assessment on an enterprise-scale networked system, correlating risk signals across 5+ domains to surface non-obvious threat patterns --- applying structured, analytical problem-solving to a live production environment.}
\resumeItem{Built data integration pipelines that stitched together incomplete, real-time threat feeds, reducing manual analyst triage effort and improving detection latency.}
\resumeItem{Identified hard limits of rule-based detection logic and authored a technical brief advocating probabilistic models; formally adopted by the team as a reference for ML-driven risk modelling.}
\resumeItem{Contributed to ML-driven anomaly detection research using behavioural threat-modelling on large-scale network infrastructure.}
\resumeItem{Delivered findings to 15+ non-technical senior stakeholders, translating statistical risk insights into clear, actionable recommendations.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{ExpenseFlow --- Full-Stack Expense Tracker} $\vert$ \emph{Next.js, TypeScript, Tailwind CSS} $\vert$ \href{https://github.com/Sowjanya12125/expensetracker}{GitHub}}{2026}
\resumeItemListStart
\resumeItem{Built a full-stack expense tracking application with Next.js 14 (App Router) and TypeScript, featuring a complete REST API (\texttt{GET/POST/PUT/DELETE}) with server-side validation and a live analytics dashboard.}
\resumeItem{Designed a repository-pattern data layer decoupling API routes from storage, enabling a one-file swap to Prisma/PostgreSQL without rewriting business logic.}
\resumeItem{Implemented category-wise donut charts and multi-month spending trend visualizations (Recharts), with type-safe data flow shared end-to-end between API, data layer, and UI components.}
\resumeItem{Shipped a responsive, accessible UI (Tailwind CSS) with optimistic delete, client-side filtering, and keyboard-navigable focus states; deployed live on Vercel.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Credit Risk \& Loan Default Prediction System} $\vert$ \emph{Python, Scikit-learn, XGBoost, SHAP}}{2025}
\resumeItemListStart
\resumeItem{Designed and deployed a modular, object-oriented binary classification pipeline for loan default prediction, achieving 87\% accuracy on held-out test data across 50K+ records.}
\resumeItem{Engineered 12+ domain-specific features --- debt-to-income ratios, payment history trends, behavioural flags --- boosting model F1-score by \raise.17ex\hbox{$\scriptstyle\sim$}9\% through systematic selection and validation.}
\resumeItem{Ran comparative evaluation across Logistic Regression, Random Forest, and XGBoost with cross-validation and probability calibration; added SHAP-based explainability to make risk scores auditable.}
\resumeItem{Built a risk-scoring module that buckets borrowers into Low / Medium / High tiers, directly supporting lending decision logic downstream.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Bayesian Uncertainty Quantification in Valuation Data} $\vert$ \emph{Python, Scikit-learn, NumPy}}{2025}
\resumeItemListStart
\resumeItem{Implemented a Bayesian Ridge Regression framework to model parameter uncertainty through posterior distributions, achieving 30--40\% tighter prediction intervals than OLS on sparse data regimes.}
\resumeItem{Built a reproducible, modular data pipeline that stress-tests model robustness across 10+ noise levels and sparsity conditions; visualised posterior distributions and credible intervals to expose high-epistemic-uncertainty cases deterministic models would mask.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Autonomous AI Agent Prototype} $\vert$ \emph{Python, REST APIs}}{Google AI Agent Day, Jul 2025}
\resumeItemListStart
\resumeItem{Led a 4-person team to architect and ship a fully functional, REST-API-integrated autonomous AI agent within a 24-hour deadline, presenting to a panel of industry judges.}
\resumeItem{Owned the API integration strategy and object-oriented, modular software design --- kept the codebase clean and maintainable under extreme time pressure, following SDLC best practices with Git-based version control.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------HACKATHONS-----------
\section{Hackathons \& Achievements}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Finalist --- Round 2, ISRO Bharatiya Antariksh Hackathon (National)}}{Jul 2025}
\resumeItemListStart
\resumeItem{Advanced to Round 2 among hundreds of nationwide teams; built high-complexity data processing algorithms for large-scale satellite and aerospace datasets and presented to ISRO evaluators.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Chaitanya Bharathi Institute of Technology (CBIT), Hyderabad}{2023 -- 2027}
{B.E. Computer Science \& Engineering --- CGPA: 8.75 / 10.0}{}
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
\resumeSubHeadingListStart
\resumeProjectHeading
{Cisco Networking Essentials --- Cisco}{Dec 2025}
\resumeProjectHeading
{Ethereum \& Solidity (Blockchain Development)}{Oct 2025}
\resumeSubHeadingListEnd

\end{document}
